---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(tregata)
library(dplyr)
```

# TregaTa

## Overview
tregata will be a (meta-)package covering waterchemistry, waterphysics and gasflux calculations.
It was initially designed for the TregaTa Project and may include some project related functions at early stages.

## Installation

```{r, eval = FALSE}
# The package is not released on CRAN yet.
# Development version from GitHub:
# install.packages("devtools")
devtools::install_github("tekknosol/tregata")
```

## Getting started
Calculate fluxes from device records and a meta file containing information about single measurements.

First check preprocessed data:
```{r, eval = TRUE}
data("gasmet", "meta")
flux_raw <- process_gasmet(gasmet, meta, pre=T)
glimpse(flux_raw)
```
Compute fluxes with:
```{r, eval = FALSE}
flux <- process_gasmet(gasmet, meta)
```
