---
title: "Compute gasfluxes from dynamic chamber measurements or BLE"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compute gasfluxes from dynamic chamber measurements or BLE}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
library(glimmr)

TRAVIS <- !identical(tolower(Sys.getenv("TRAVIS")), "true")
knitr::opts_chunk$set(purl = TRAVIS)
```

glimmr is an R package that makes it easier to process and handle data from 
dynamic flux measurements and provides functions to use with the boundary layer 
Equation (BLE).

# (Dynamic-) chamber measurements
## Approach
During applications of dynamic chambers, typically two kinds of datasets are
created: One continous dataset, provided by the gas analyzer, containing the gas
mixing ratios and one
metadataset with information about the single chamber applications. Typically this 
contains an ID of the spot location, time of the measurement start (and end) and
maybe the chamber temperature.

glimmr reads both datasets, slices the concentration data into chunks defined by
the metadata and fits linear and robust linear models (`robust::lmRob`) for the actual flux 
calculation.

The datastructure of the recorderd data can be widely defined, hence glimmr is 
not restriced to a speceific device.
Nevertheless, wrapper functions are included for GASMET and LosGatos gas
analizers.

## Read data
GASMET and LosGatos records can be directly loaded:
```{r, eval=FALSE}
gasmet <- read_gasmet("path/to/gasmet_file.csv")

losgatos <- read_losgatos("path/to/losgatos/dir")
losgatos <- read_losgatos("path/to/losgatos_file.txt")
```
Single LosGatos files, as well as directories containing zips and txt files are
supported. See `read_losgatos()` for details.

The structure of corresponding metdata is defined as follows:
```{r echo=TRUE}
meta_gasmet

meta_losgatos
```

## Process fluxes
To use any arbitrary device all columns containing used information need to be
defined.
```{r, eval=TRAVIS}

# setup analyzer
custom_analyzer <- analyzer(
  #define datastructure
  time_stamp = "Time",
  conc_columns = c(CH4 = "[CH4]_ppm", CO2 = "[CO2]_ppm"),
  preassure = "GasP_torr",
  preassure_factor = 1.33322,
  temperature = "AmbT_C",
  trimmer = trim_time,
  # define metadata structure
  plot = "plot",
  date = "date",
  start = "start",
  end = "end",
  #define chamber dimensions
  V = 0.01461,
  A = 0.098
)

# compute fluxes
process_chamber(
  # specify data
  data = losgatos, 
  meta = meta_losgatos,
  #specify analyzer
  analyzer = custom_analyzer
)
```

For simplification, GASMET and LosGatos can be called via convenient
wrapper functions:

```{r, eval=FALSE}
process_losgatos(losgatos, meta_losgatos)

process_gasmet(gasmet, meta_gasmet)
```

While the start of single measurements is (usually) defined by a known point
in time, the end can be defined in different ways. See `process_chamber()` for 
details.
